% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Rui Zhou}

\basicInfo{
  \email{zhour2@student.unimelb.edu.au} \textperiodcentered\ 
  \phone{(+61) 0478663333} \textperiodcentered\ }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Melbourne}, Melbourne, Australia}{2018 -- Present}
\textit{Master student} in Information Technology (IT)\\
\textit{Weight. Average} 91/100
\datedsubsection{\textbf{East China Normal University (ECNU)}, Shanghai, China}{2013 -- 2017}
\textit{Bachelor student} in Computer Science and Technology (CS)\\
\textit{GPA} 3.54/4.0

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Nim Game Project}}{Mar. 2018 -- May. 2018}
\role{Java}{Individual Projects}
Brief introduction: A Nim game system
\begin{itemize}
  \item Containd two types of Nim games
  \item Containd AI Nim player
\end{itemize}

\datedsubsection{\textbf{Cicso} Shanghai, China}{2016 -- 2016}
\role{Intern}{}
Brief introduction: Product testing

\datedsubsection{\textbf{Gobang AI Project}}{Oct. 2015 -- Nov. 2015}
\role{C++}{Individual Projects}
Brief introduction: An Implementation of Gobang AI
\begin{itemize}
  \item Used MinMax Search
  \item Used alpha–beta pruning
\end{itemize}

\datedsubsection{\textbf{DiskToy Project}}{Sep. 2015 -- Nov. 2015}
\role{C++}{Collaborated with Chenyang Liu}
Brief introduction: A tool used to anaylse disk usage
\begin{itemize}
  \item Used DFS to explore all dictionaries and files in given path
  \item Used the graphical form of the Treemap to show the results
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Bronze Medal}, Award on The ACM-ICPC Asia Regional Contest EC-final Site 2015}{Dec. 2015}
\datedline{\textit{Bronze Medal}, Award on The ACM-ICPC Asia Regional Contest Changchun Site 2015}{Oct. 2015}
\datedline{\textit{Bronze Medal}, Award on The ACM-ICPC Asia Regional Contest Shanghai Metropolitan Site 2015}{Oct. 2015}
\datedline{\textit{Bronze Medal}, Award on The ACM-ICPC Asia Regional Contest Shanghai Site 2014}{Dec. 2014}
\datedline{\textit{Bronze Medal}, Award on The ACM-ICPC Asia Regional Contest Shanghai Site Invitational 2014}{Jul. 2014}

\section{\faCogs\ Programming Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, C++, Java
  \item Development: Console program
\end{itemize}

\section{\faInfo\ Language Skills}
\begin{itemize}[parsep=0.5ex]
  \item ITLTS
  \item Listening: 7.0 Reading: 7.0 Writing: 5.5 Speaking: 5.5
  \item Overall: 6.5
\end{itemize}

%\section{\faStar\ Preference Aspects}
%\begin{itemize}[parsep=0.5ex]
%  \item Data mining
%  \item Machine learning
%  \item Artificial intelligence
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
